% NOTE: this file requires the accompanying res.cls file in this repo
\documentclass[margin]{res}
\setlength{\textwidth}{5.3in} % set width of text portion

\begin{document}

\moveleft.5\hoffset\centerline{\Large\bf Innes Anderson-Morrison}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{York, UK}
\moveleft.5\hoffset\centerline{innes.andersonmorrison@gmail.com}
\moveleft.5\hoffset\centerline{https://github.com/sminez}


\begin{resume}
 
\section{SUMMARY}
I am a senior software engineer and engineering manager with a proven track record in
designing, implementing and delivering reliable back end web services and developer
tooling. I am passionate about designing and building systems that compose well.

Currently I am in charge of an internal enablement team developing systems to support
and accelerate engineering teams at Anaplan. The tooling I write has dramatically
improved the company's release cadence, supportability of production systems and
day to day work experience of our engineers.

Outside of work I develop open source software and carry out research into Clifford
Algebras and fundamental physics as part of the Quicycle society.


\section{EDUCATION}
{\sl Bachelor of Engineering,} \hfill University of Glasgow, 2006 - 2010 \\
Audio and Video Electronic Engineering \\
{\sl PGCE,} \hfill University of Manchester, 2012 - 2013 \\
Teacher of Mathematics and Physics


\section{SKILLS}
Software architecture, API design, back-end web services, developer documentation. \\
Rust, Go, Python, Posix Shell, SQL, Groovy, GraphQL, AWS, Docker, Kubernetes, Jenkins.


\section{EXPERIENCE}
{\sl Software Engineering Manager} \hfill Nov 2021 - Present  \\
Anaplan, York UK.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item A combined Manager and Technical Lead position to
        maintain autonomy and support the team's ability to react
        quickly to changing user needs.
  \item Responsible for the team's roadmap, prioritisation of incoming
        work and overall design and implementation of our systems.
\end{itemize}

{\sl Senior Software Engineer} \hfill Nov 2020 - Present  \\
Anaplan, York UK.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Promoted following the success and adoption of the tooling and
        services developed to support Anaplan engineering teams with
        their path to production.
  \item Further increased release velocity to now be shipping changes
        daily for dozens of independent services.
\end{itemize}

{\sl Software Engineer} \hfill Jan 2019 - Nov 2020 \\
Anaplan, York UK.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Tech lead for a small enablement team driving improvements to
        the build and release process of Anaplan's New User Experience.
  \item Improved a monthly release cadence down to multiple releases per
        week through development of tooling and automation to support the
        release process.
\end{itemize}

{\sl Technical Specialist Software Developer} \hfill Feb 2018 - Jan 2019 \\
Stockholm Environment Institute, York UK.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Development and operation of multiple full-stack web services written
        in Python (Django) and JavaScript.
  \item Development of a mathematical analysis plugin for the LEAP IBC program
        used for modelling climate impact from pollutants.
\end{itemize}

{\sl Software Engineer} \hfill May 2016 - Feb 2018 \\
Cocoon Labs, York UK.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Back end web development using Python and Go along with DevOps work based
        primarily around writing and maintaining multiple services deployed to AWS.
  \item Creation of developer tooling, data analysis, database management and
        report generation.
\end{itemize}



\section{ADDITIONAL \\ PROJECTS}             
{\sl The Penrose window manager library} \hfill Jun 2020 - Present \\
https://github.com/sminez/penrose
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item I am the author and maintainer of the Penrose X11 window
        manager library on GitHub. The library, documentation and accompanying
        video series allow users to write their own fully customised tiling
        window manager in Rust.
\end{itemize}

{\sl The Quicycle Society} \hfill Mar 2016 - Present \\
https://quicycle.com
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item I am a researcher and board member of the Quicycle Society lead by
        Dr John G. Williamson. The society works to advance our understanding
        of fundamental Physics through the development of analytic, testable
        theories.
  \item My role in the society is around the development of a modified Clifford
        algebra to enable efficient, analytic calculation of physical processes.
        As a related endeavour, I also work to produce software that aids our
        researchers and allow for direct modelling of the theory so it may be
        compared to experimental results.
\end{itemize}

\end{resume}
\end{document}
